---
title: "CSV Process Package"
author: "Cheng-Chung Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CSV Process Package}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

## Installing necessary packages
Install some packages first in order to run the proposed package.
```{r}
install.packages(c("dplyr", "readr","tidyr","maps","graphics"),repos = "http://cran.us.r-project.org")
library(readr)
library(dplyr)
library(tidyr)
library(maps)
library(graphics)
```

## Accessing the package
```{r}
library(devtools)
install_github("askia318/CSVProcess")
library(CSVProcess)
```

## Introduction 
This package contains five functions: fars_read, make_filename, fars_read_years, fars_summarize_years, and fars_map_state. They are functions to read and process CSV file and we will introduce them respectively.

## fars_read

This is a simple function which first reads 'filename' file in the working directory and
then outputs it as a tibble. You can input filename (using the \code{filename} argument).
It the file does not exist in the working directory, the function will stop and print an
error message; otherwise the function will call 'read_csv' function in "readr" package and
'tbl_df' function in "dplyr" package to read and transform the file into a tibble.

An example: 
```{r}
fars_read("data/accident_2013.csv.bz2")
```

## make_filename

The function will transfer the year you input into an integer and output as a character
named "accident_'year'.csv.bz2". You can input the year using \code{year} argument.

```{r}
make_filename(2013)
```

## fars_read_years

The function will read files in the form "accident_'year'.csv.bz2" where 'year' is inputted
by user, read the data as a tibble and then select columns 'MONTH' and 'year' as output.
If file "accident_'year'.csv.bz2" does not exist, it will print a warning message and return
NULL. You can input the year using \code{list(years)} argument.

```{r}
years <- list(2013,2014)
fars_read_years(years)
```

## fars_summarize_years
This function calls fars_read_years to read files in "accident_'year'.csv.bz2" form and
outputs a tibble with column 'MONTH' and 'year' first. Then it unlists (MONTH, year) pairs,
groups them, and counts their numbers. Finally, it "reshapes" the output as a tibble
with "MONTH", "years" form where "years" is the list in the input.
You can input the year using \code{list(years)} argument.

```{r}
years <- list(2013,2014)
fars_summarize_years(years)
```

## fars_map_state
The function first transfers the input 'year' into a character as "accident_'year'.csv.bz2"
and read the file "accident_'year'.csv.bz2" as a tibble valued as 'data', then it also
transfers the input state.num' as an integer. Moreover, if the field 'data$STATE' does not
contain 'state.num', the function will stop and print a message.
If data$STATE contains state.num but has nothing to plot, the function will print
"no accidents to plot" and return invisible diagram; otherwise the function will plot
a diagram with LONGITUD in x-asix and LATITUDE in y-asix with points to indicate the
distrubution. You can input the year using \code{state.num,year} argument.

```{r}
fars_map_state(42,2013)
```
