---
title: "CSV Process Package"
author: "Cheng-Chung Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CSV Process Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package contains five functions: fars_read, make_filename, fars_read_years, fars_summarize_years, and fars_map_state. They are functions to read and process CSV file and we will introduce them respectively.


## fars_read

This is a simple function which first reads 'filename' file in the working directory and
then outputs it as a tibble. You can input filename (using the \code{filename} argument).
It the file does not exist in the working directory, the function will stop and print an
error message; otherwise the function will call 'read_csv' function in "readr" package and
'tbl_df' function in "dplyr" package to read and transform the file into a tibble.

An example: 
```{r}
fars_read("accident_2013.csv.bz2")
```

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
